HW2_aengstrom28
===============

# Getting data
source("http://bioconductor.org/biocLite.R")
library(Biobase)
library(data.table)
library(GEOquery)
library(limma)
gse_new <- getGEO("GSE40812")
```
set working directory to source file location
```{r}
#Cleaning up data
gds <- gse_new
pd <- pData(gds)
mm_pd <- pd[pd$source_name_ch1=="Monocyte-derived Macrophage",]
mm_eset <- gds[,rownames(mm_pd)]
mm_pd$HCV <- gsub(".*: ", "", mm_pd$characteristics_ch1)
mm_pd$HCV <- ifelse(mm_pd$HCV=="Neg", "-", "+")
mm_pd$treatment <- gsub(".*: ", "", mm_pd$characteristics_ch1.2)
```

```{r}
#Setting up design matrix for limmma to test for differential expression between poly IC and mock treated groups at p-value < 0.1
treat_matrix <- model.matrix(~treatment+0, mm_pd)
colnames(treat_matrix)
colnames(treat_matrix) <- c("Mock", "Poly")
fit2 <- lmFit(mm_eset, treat_matrix)
fit2 <- eBayes(fit2)
```

```{r}
#Top table of results, adjusted for false discovery rate (5%)
TopTable2 <- topTable(fit2, coef="Poly", number=Inf, adjust="BH")
sum(TopTable2$adj.P.Val < 0.1)
```

```{r}
#Make new eset using the 47323 probes that are differentially expressed between poly Ic and mock treatments and set-up a new design matrix to test for statistically significant (p-value <0.1) change in expression between HCV+ and HCV- patients
eset_small <- mm_pd[TopTable2$adj.P.Val < 0.1,]
HCV_matrix <- model.matrix(~0+HCV, eset_small)
colnames(HCV_matrix)
colnames(HCV_matrix) <- c("Neg", "Pos")
fit7 <- lmFit(mm_eset, HCV_matrix)
fit7_ebay <- eBayes(fit7)
TopTable7 <- topTable(fit7_ebay, coef="Neg", adjust="BH")
sum(TopTable7$adj.P.Val < 0.1)
```
